Considering scale in multilayer animal social networks

### 2020-08-26 paper/manuscript.Rmd
add refs

# Introduction
Our inferences regarding the processes underlying ecological patterns
are directly linked to the scale at which they are observed [@Levin_1992;
@Allen_2015]. Animals are influenced across scales by ecological processes such as
trophic interactions, resource availability
[@Legendre_1993; @Chave_2013], and global climate and productivity [@Field_2009].
Multiscale ecology has been integrated into species distribution modelling
[@Elith_2009], habitat selection [@Mayor_2007], and food webs [@Sugihara_1989].
We posit that it is important to consider the scale dependence of 
animal behaviour within the social environment to effectively understand 
complex social systems.

>>>>

# Introduction
Our inferences regarding the processes underlying ecological patterns
are directly linked to the scale at which they are observed [@Levin_1992;
@Allen_2015]. Animals are influenced across scales by ecological processes such as
trophic interactions, resource availability
[@Legendre_1993; @Chave_2013], and global climate and productivity [@Field_2009].
Multiscale ecology has been integrated into species distribution modelling
[@Elith_2009], habitat selection [@Mayor_2007], and food webs [@Sugihara_1989].
We posit that it is important to consider the scale dependence of 
animal behaviour within the social environment to effectively understand 
complex social systems [@Whitehead_2008; @Webber_2018].
